---
title: "htcDataUseExploration24012019"
author: "John Alan Willis"
date: "1/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This document is an experimental testbed for combining the data.tree package with various vizualization tools 

first we'll load a bunch of packages

```{r loadPackages}
library(data.tree)
library(collapsibleTree)
library(tidyverse)
library(splitstackshape)
library(treemap)
library(d3treeR)
library(r2d3)
library(networkD3)
```


Next we'll build a simple df from the project directory structure 
this is exactly like the example shown at https://cran.r-project.org/web/packages/data.tree/vignettes/applications.html#file-explorer-system-utilities

```{r readInFileStructure}
path <- "../.."
files <- list.files(path = path, 
                    recursive = TRUE,
                    include.dirs = FALSE) 

df <- data.frame(
      filename = sapply(files, 
                        function(fl) paste0("data.tree","/",fl)
      ), 
      file.info(paste(path, files, sep = "/")),
      stringsAsFactors = FALSE
    )
 
print(head(df)[c(1,2,3,4)], row.names = FALSE)


```


having generated the DF, lets now incorporate it into a tree

```{r createDataTree}
fileStructure <- as.Node(df, pathName = "filename")
fileStructure$leafCount / (fileStructure$totalCount - fileStructure$leafCount)

print(fileStructure, "mode", "size", limit = 25)
plot(fileStructure)

#plot with networkD3
fileStructureList <- ToListExplicit(fileStructure, unname = TRUE)
radialNetwork(fileStructureList)

```


```{r filteredSummary}
filteredSummary <- filter(fileSummary, FileSizeBytes > 20000000)
filteredTree <- as.Node(filteredSummary, pathName = "Filepath")
print(filteredTree, limit = 40)
plot(filteredTree)


#plot with networkD3
fileStructureList <- ToListExplicit(filteredTree, unname = TRUE)
radialNetwork(fileStructureList)
```
next lets make a tree with the actual from mobydisk

```{r testDataVizout}
fafqbamList <- read_delim('../../outputs/2019-01-18/findFaFqBamOutputHumanReadable.txt', " ")
directoriesList <- read_tsv('../../outputs/2019-01-18/directoriesList24012019.txt')
fileSummary <- read_tsv('../../outputs/2019-01-18/fullFileSummarySortedBySize.tsv')
filteredFileSummary <- fileSummary %>%
  filter(FileSizeBytes >100000)
fileSummarTree <- as.Node(filteredFileSummary, pathName = 'Filepath')

print(fileSummarTree, "mode", "size", limit = 25)
plot(fileSummarTree)

#plot with networkD3
fileStructureList <- ToListExplicit(fileStructure, unname = TRUE)
radialNetwork(fileStructureList)
```

lets do a treemap by converting the filteredTree to a tidy df with columnar hierarchy designation

```{r treemap}

fileSummForTreemap <- ToDataFrameTypeCol(filteredTree)
head(fileSummForTreemap)

fileSummForTreemap2 <- cSplit(fileSummary, "Filepath", sep = '/')
#fileSummForTreemap2[,12:18] <- as.character(fileSummForTreemap2[,12:18])
fileSummForTreemap2[] <- lapply(fileSummForTreemap2, as.character)
fileSummForTreemap2[,"FileSizeBytes"] <- lapply(fileSummForTreemap2[,"FileSizeBytes"], as.double)
columnsOfInterest <- paste0('Filepath_', 10:24)
treemap(fileSummForTreemap2[FileSizeBytes >= 1000000,], index = columnsOfInterest[1:4], vSize = 'FileSizeBytes', type='index')

```


letes build a full viz script

```{r dataVizScript}
fileSummary <- read_tsv('fullFileSummarySortedBySize.tsv')

fileSummForTreemap2 <- cSplit(fileSummary, "Filepath", sep = '/')

fileSummForTreemap2[] <- lapply(fileSummForTreemap2, as.character)
fileSummForTreemap2[,"FileSizeBytes"] <- lapply(fileSummForTreemap2[,"FileSizeBytes"], as.double)


columnsOfInterest <- paste0('Filepath_', 10:24)
treemap(fileSummForTreemap2[FileSizeBytes >= 100000,], index = columnsOfInterest[1:4], vSize = 'FileSizeBytes', type='index')
d3treeout <- d3tree2(treemap(fileSummForTreemap2[FileSizeBytes >= 100000,], index = columnsOfInterest[1:7], vSize = 'FileSizeBytes', type='index'), root = 'jaw212')

save_d3_html(d3treeout, file = "JAWFileStructureViz.html", selfcontained = TRUE)
```


```{r visualizeByUser}
nolanSummary <- fileSummary %>%
  filter(grepl("nolan", User), FileSizeBytes > 10000 )

filteredTree <- as.Node(nolanSummary, pathName = "Filepath")

fileSummForTreemap <- ToDataFrameTypeCol(filteredTree)
head(fileSummForTreemap)

fileSummForTreemap2 <- cSplit(nolanSummary, "Filepath", sep = '/')
#fileSummForTreemap2[,12:18] <- as.character(fileSummForTreemap2[,12:18])
fileSummForTreemap2[] <- lapply(fileSummForTreemap2, as.character)
fileSummForTreemap2[,"FileSizeBytes"] <- lapply(fileSummForTreemap2[,"FileSizeBytes"], as.double)
columnsOfInterest <- paste0('Filepath_', 10:24)
treemap(fileSummForTreemap2[FileSizeBytes >= 100000,], index = columnsOfInterest[1:4], vSize = 'FileSizeBytes', type='index')

d3treeout <- d3tree2(treemap(fileSummForTreemap2[FileSizeBytes >= 100000,], index = columnsOfInterest[1:7], vSize = 'FileSizeBytes', type='index'), root = 'jaw212')

save_d3_html(d3treeout, file = "JAWFileStructureViz.html", selfcontained = TRUE)


```

Lets more formally explore this dataset

```{r exploreExperiments}
colnames(fileSummary)
colnames(directoriesList) <- "Filepath"
directoriesList2 <- directoriesList %>%
  data.frame() %>%
  mutate(Filepath=as.character(Filepath)) %>%
  mutate(Filepath=map(.$Filepath, str_replace, pattern = "......", replacement =  "/mnt/mobydisk/pan/genomics/data/alee/"))

head(directoriesList)
dim(directoriesList)

colnames(fafqbamList) <-c("fileSize", "Filepath")

fafqbamList2 <- fafqbamList %>%
  data.frame() %>%
  mutate(Filepath=as.character(Filepath)) %>%
  mutate(Filepath=map(.$Filepath, str_replace, pattern = "......", replacement =  "/mnt/mobydisk/pan/genomics/data/alee/"))



#first filter the full fileSummary dataframe by keeping only directories

directoriesSummary <- fileSummary[fileSummary$Filepath %in% directoriesList2$Filepath,]
#directoriesSummary <- inner_join(fileSummary, directoriesList2)

byUserDiskUseSummary <- directoriesSummary %>%
  group_by(User) %>% 
  summarize("Size"=sum(FileSizeBytes)) 

ggplot(byUserDiskUseSummary) +
  geom_col(mapping = aes(User, Size)) +
  coord_flip()
  
byUserFileCountSummary <- directoriesSummary %>%
  group_by(User) %>% 
  summarize("Files"=n()) 

ggplot(byUserFileCountSummary) +
  geom_col(mapping = aes(User, Files)) +
  coord_flip()

joinedDUFC <- full_join(byUserDiskUseSummary, byUserFileCountSummary) %>%
  mutate(ratio=Size/Files)

ggplot(joinedDUFC) +
  geom_point(mapping = aes(Size, Files, color=User))
             
```

```{r exploreByUser}

```